---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This guide will show you how to gather data from the Kolada API and use the Shiny app to help us interact/dispay the data.

## Load the package

```{r setup}
library(lab5)
```

## get_kpi_group function

In this function we select a specific KPI group we want to explore. And under here we have selected the KPI group GKPI127 and printed out the first 5 ID:s and Titles of the group. The KPIs selected here is used in the Shiny app.

```{r get_kpi_group}
kpi_group <- get_kpi_group("GKPI127")
kpi_members <- rbind.data.frame(kpi_group$members)
kpi_members[1:5, ]

```

## get_municipalities function

This function creates a data frame of all the municipalities in the KPI and filter out the regions that also is inside the KPI. This is used in the Shiny app UI and below there is the first 5 municipalities from the KPI.

```{r get_municipalities}
head(get_municipalities())

```

## get_data function

This is an example of how get_data function works. The function fetches data from a specific KPI, municipality and year. So under here we get a data frame for the values divided by gender of the KPI data (N09890), municipality (Helsingborg) and the year (2019) selected.

```{r get_data}
get_data("N09890", "Helsingborg", "2019")

```

## Shiny app
```{r ,eval=FALSE}
app()
```
